---
title: "Group report"
author: "Group 4"
date: '2022-08-02'
output: github_document
  # html_document:
  #     fig_caption: true
  

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
# source("code/vikesland/cleaning_vikesland.R")
```

# Cleaning

## Fluxes

A flux that requires cleaning:
```{r, echo=FALSE, fig.align='left', fig.cap=""}
co2_cut_vikesland_60_flux233
```


A flux that does not require cleaning:
```{r, echo=FALSE, fig.align='left', fig.cap=""}
co2_cut_vikesland_60_flux105
```



## PAR values

Problems with PAR values during ER measurements:
```{r, echo=FALSE, fig.align='left', fig.cap=""}
PAR_wrong_duringER_plot
```


Problems corrected. The negative PAR values were replaced by 0 (because it is ER):
```{r, echo=FALSE, fig.align='left', fig.cap=""}
PAR_right_duringER_plot
```

# Data dictionaries
## Fluxes

```{r, echo=FALSE}
knitr::kable(cflux_vikesland_dic)
```

# Calculations
## Fluxes

<img src="https://render.githubusercontent.com/render/math?math=\color{violet}flux=slope\times \frac{P\times V}{R\times T\times A}">

Where:

- flux: the flux of CO~2~ at the surface of the plot ($\mu$mol m^-2^ s^-1^)
- slope: slope of linear regression fitting the CO~2~ concentration versus time ($\mu$mol mol^-1^)
- P: pressure, assumed 1 atm
- V: volume of the chamber and tubing (L)
- R: gas constant (0.082057 L atm K^-1^ mol^-1^)
- T: chamber air temperature (K)
- A: area of chamber frame base (m^2^)

## Gross primary productivity

GPP = NEE - ER
